---
title: "Class 15 Pathway Analysis and Gene List Interpretation"
author: "Darren Lam"
date: "11/14/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Pathway analysis

An enriched pathway results from the overlap between differentially expressed genes (DEGs) and known pathways (genesets)

Limitations to pathway analysis include: geneset annotation bias, non-model organisms, ignoring post-transcriptional regulation, tissue-specific vatiations not annotated, size bias


### Overview

1) You have a list of genes/proteins of interest (and info on fold change, p-value, spectral counts, presence/absence)
2) Translate to appropriate identifier (e.g. UniProt, Entrez, etc) using merge() or mapIds()

# Hands-on worksheet

Reading in our colData and countData
```{r}

colData = read.csv("GSE37704_metadata.csv", row.names = 1)
head(colData)

countData = read.csv("GSE37704_featurecounts.csv", row.names = 1)
countData <- as.matrix(countData[,-1]) # removed first column so countData columns match colData rows
head(countData)
```

Making sure our row labels in colData match our column labels in countData
```{r}

rownames(colData)
colnames(countData)

all (rownames(colData) == colnames(countData))
```

Removing zero-values from our dataset
```{r}
# Identifying which points in the dataframe are zero values
zero.vals <- which(countData[,1:6]==0, arr.ind=TRUE)
head(zero.vals)

# Identifying rows with zero values
to.rm <- unique(zero.vals[,1])

# Removing the rows with zero values from our dataset
mycounts <- countData[-to.rm,] # new dataset: mycounts
head(mycounts)
```

