---
title: "class08"
author: "Darren Lam"
date: "10/24/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Class 8: Machine Learning pt. 1

### Sample data
```{r}
# Generate some example data for clustering
tmp <- c(rnorm(30,-3), rnorm(30,3))
x <- cbind(x=tmp, y=rev(tmp))
plot(x, main = "sample cluster data")
```

### Using the kmeans() on our sample data
```{r}
k <- kmeans(x, centers = 2, nstart = 20)
```

### Inspecting results
```{r}
k
```

### Identifying the cluster size, assignment/membership, and centers
```{r}
k$size
k$cluster
k$centers
```

### Plotting x colored by the kmeans cluster assignment with cluster centers as blue points
```{r}
plot(x, main = "sample cluster data", col = k$cluster)
points(k$centers, col = "blue", pch = 15)
```

## Hierarchical clustering in R
The hclust() function  requires a distance matrix as imput. You can get this from the dist() function
```{r}
# First we need to calculate point (dis)similarity
#   as the Euclidean distance between observations
dist_matrix <- dist(x)

# The hclust() function returns a hierarchical
#  clustering model
hc <- hclust(d = dist_matrix)

# the print method is not so useful here
hc
```

Plotting our heirarchical clustering
```{r}
# Draws a dendrogram
plot(hc)
```

Cutting our tree
```{r}
plot(hc)
abline(h = 6, col = "red")
grps <- cutree(hc, h = 6)
```

Heirarchichal clustering with more complex data
```{r}
# Step 1. Generate some example data for clustering
x <- rbind(
  matrix(rnorm(100, mean=0, sd = 0.3), ncol = 2),   # c1
  matrix(rnorm(100, mean = 1, sd = 0.3), ncol = 2), # c2
  matrix(c(rnorm(50, mean = 1, sd = 0.3),           # c3
           rnorm(50, mean = 0, sd = 0.3)), ncol = 2))
colnames(x) <- c("x", "y")

# Step 2. Plot the data without clustering
plot(x)

# Step 3. Generate colors for known clusters
#         (just so we can compare to hclust results)
col <- as.factor( rep(c("c1","c2","c3"), each=50) )
plot(x, col=col)
```

```{r}
kmeans(x, centers = 3, nstart = 20)
```

```{r}
# clustering
hc <- hclust(dist(x))

# drawing tree
plot(hc)
abline(h = 2, col = "red")

# cutting tree into clusters
grps <- cutree(hc, k = 3)

```

Plot the data colored by their hclust result with k=3
```{r}
plot(x, col = grps)
```

How many points in each cluster?
```{r}
table(grps)
```

Cross-tabulate i.e. compare our clustering results with the known answer
```{r}
table(grps, col)
```

# PCA

```{r}
mydata <- read.csv("https://tinyurl.com/expression-CSV",
row.names=1)

head(mydata)

dim(mydata)
```

Doing PCA with the prcomp() function
```{r}
pca <- prcomp(t(mydata), scale=TRUE)
attributes(pca)

pca$x
```

A basic PC1 PC2 2-D plot
```{r}
plot(pca$x[,1], pca$x[,2])
```

Percent variance
```{r}
pca.var <- pca$sdev^2
pca.var.per <- round(pca.var/sum(pca.var)*100, 1)

pca.var.per # imagine the scree plot

 barplot(pca.var.per, main="Scree Plot", # the actual scree plot
 xlab="Principal Component", ylab="Percent Variation")
```

Making our plot more useful
```{r}
## A vector of colors for wt and ko samples
plot(pca$x[,1], pca$x[,2], 
     col=c("red", "red", "red", "red", "red", "blue", "blue", "blue", "blue", "blue"))
```

# PCA of UK food data

```{r}
x <- read.csv("UK_foods.csv")

dim(x)
```

Fixing our row names
```{r}
x <- read.csv("UK_foods.csv", row.names=1)
head(x)
```

Plotting the data without PCA
```{r}
barplot(as.matrix(x), beside=T, col=rainbow(nrow(x)))
```

Pairwise plots
```{r}
pairs(x, col=rainbow(10), pch=16)
```

Using PCA
```{r}
# Use the prcomp() PCA function 
pca <- prcomp( t(x) )
summary(pca)
pca
```

```{r}
# Plot PC1 vs PC2
plot(pca$x[,1], pca$x[,2], xlab="PC1", ylab="PC2", xlim=c(-270,500))
text(pca$x[,1], pca$x[,2], colnames(x), col=c("yellow", "red", "blue", "green"))
```

```{r}
v <- round( pca$sdev^2/sum(pca$sdev^2) * 100 )
v
```

