---
title: "class06 R functions"
author: "Darren Lam"
date: "10/17/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is my work from class06 in **BIMM 143**.

# Using code chunks

```{r}
# Demoing a code chunk

plot(1:10, main = "Test plot")
```


# Practice reading files (again...)

Reading comma-separated files

```{r}
read.csv("test1.txt", header = T)
```

Reading $-separated files

```{r}
read.table("test2.txt", sep = "$", header = T)
```

Reading space-separated files

```{r}
read.table("test3.txt", col.names = c("Col1", "Col2", "Col3"))
```

# Writing a simple function

Writing an add function
```{r}
add <- function(x, y = 1) {x + y}
```

Playing with our add function
```{r}
add(1)
add(x=1, y=4)
add( c(1,2,3) )
add( c(1,2,3), 4 )
```

# Writing a more interesting function

Writing a rescale function

```{r}
rescale <- function(x) {
   rng <-range(x)
   (x - rng[1]) / (rng[2] - rng[1])
}
```

**Test 1:** A small example where we know the answer

```{r}
rescale(1:10)
```

**Test 2:** How would we get our function to work here..?

```{r}
rescale( c(1,2,NA,3,10) )
```

**Solution:** We have our range function remove NA values by modifying the arguments

```{r}
rescale2 <- function(x) {
   rng <-range(x, na.rm = T)
   (x - rng[1]) / (rng[2] - rng[1])
}

rescale2( c(1,2,NA,3,10) )
```

# Section 2 of hands-on sheet

Install the **bio3d** package for sequence and structure analysis

```{r}
#install.packages("bio3d")
```

```{r}
library(bio3d)
s1 <- read.pdb("4AKE")  # kinase with drug
s2 <- read.pdb("1AKE")  # kinase no drug
s3 <- read.pdb("1E4Y")  # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

## Documentation:
**comments on what are the inputs to the function:**
The inputs to the function are PDB files.

**what the function does and how to use it:**
This function 
