---
title: "class06_HW"
author: "Darren Lam"
date: "10/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is my homework for BIMM 143 **Class 06**.

# Can you improve this analysis code?
```{r}
library(bio3d)
s1 <- read.pdb("4AKE")  # kinase with drug
s2 <- read.pdb("1AKE")  # kinase no drug
s3 <- read.pdb("1E4Y")  # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

## Step 1: Removing copy and paste errors
```{r}
library(bio3d)
s1 <- read.pdb("4AKE")  # kinase with drug
s2 <- read.pdb("1AKE")  # kinase no drug
s3 <- read.pdb("1E4Y")  # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA") # s1 changed to s3 in argument

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

## Step 2: Simplify to work with a generic vector named “x”
```{r}
library(bio3d)
  
  x <- read.pdb("4AKE")
  
  x.chainA <- trim.pdb(x, chain = "A", elety = "CA")
  
  x.b <- x.chainA$atom$b
  
  plotb3(x.b, sse = x.chainA, typ = "l", ylab = "Bfactor")
```

## Step 3: Turn it into a function — plot.bfac()
```{r}
#plot.bfac allows you to plot the B-factor for each amino acid residue in a protein's A chain.

plot.bfac <- function(x) {  # input is PDB accession number
  
  y <- read.pdb(x)  # PDB file is read
  
  # variables assigned to amino acid residues and associated B-factors
  y.chainA <- trim.pdb(y, chain = "A", elety = "CA")
  y.b <- y.chainA$atom$b
  
  # output is a line plot of the B-factors of each amino acid residue
  plotb3(y.b, sse = y.chainA, typ = "l", ylab = "Bfactor", main = x)
  
}
```

## Step 4: Testing our new function, plot.bfac()!
```{r}
plot.bfac("4AKE")
plot.bfac("1AKE")
plot.bfac("1E4Y")
```

# Grading rubric:

## Documentation:
1 pt - comments on what are the inputs to the function. 

1 pt - what the function does and how to use it.

1 pt - what is the output of the function.

## Code:
2 pt - function behaves as desired, producing the correct output and follows assignment
specifications.

2 pt - the code is efficient meaning it uses best practices such as limiting calculation duplication.

2 pt - code is readable, meaning best practices are used including proper indentation and whitespace used, relevant variable names, and organized in a logical manner.

1 pt - function code and call executes and is working properly.
